{\bf {\Large Title....}}

### 2016-07-11 ident_manu.Rnw
p1z1 ident fig done

Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differenceses between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group.

@@

% identifiability boxplot, p1, z1 only
<<p1z1identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group. Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category. Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 10, fig.width = 4, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
data(p1z1cat_ident)
data(p1z1top_ident)

@@

@@

p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank()
  ) + 
  theme(legend.position = 'none') +
  ggtitle('(a) By parameter category')

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 1, heights = c(0.5, 1)),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)

>>>>

Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).

@@

% identifiability boxplot, p1, z1 only
<<p1z1identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group. Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category. Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 8, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.5\\textwidth'>>=
data(p1z1cat_ident)
data(p1z1top_ident)

@@

p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  scale_x_continuous(limits = c(1, 20)) +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank()
  ) + 
  theme(legend.position = 'none') +
  ggtitle('(a) By parameter category')

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  scale_x_continuous(limits = c(1, 20)) +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank(), 
    legend.title = element_blank()
  ) + 
  ggtitle('(b) By top parameters, all categories')

@@

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth

grid.arrange(
  arrangeGrob(pA, pB, ncol = 1, heights = c(0.45, 1)),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.15)
)
